Portfolios of Subgraph Isomorphism Algorithms

### 2015-12-16 paper/paper.tex
mention that incomplete LAD isn't included in portfolio
Gnuplotify cumulative plot
We shall kill 6.1. With fire! And blood!

\usepackage{times}
\usepackage{complexity}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage{xcolor,colortbl}
\usepackage{tabularx}
\usepackage{siunitx}
\usepackage{xspace}
\usepackage{scalefnt}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[sort]{cite}
\usepackage{enumitem}
\setlist{nosep}

@@

\begin{figure}[t]
\includegraphics[width=\textwidth]{courbe.pdf}
\caption{Number of solved instances over CPU time for the eight algorithms we
consider in this paper, and the virtual best solver (VBS) that shows the best
solver on an instance by instance basis.\label{expTimeGraph}}
\end{figure}

@@

@@

\subsection{Portfolios for Different Timeouts}

The question arises of whether the success of our approach is limited to the
particular timeout we have chosen. Table~\ref{tab:resTimeouts} shows the
performance of our algorithm selection approach for timeouts ranging from $10^2$
to $10^8$. We do not include the instances solved by \IncompleteLAD and \VFtwo
presolving here, as these components do not change for different timeouts.

\begin{table}[ht]
\centering
\begin{tabular}{llrrr}
  \toprule
timeout & solver & mean MCP & solved instances & mean performance\\
  \midrule
$10^2$ & virtual best & 0 & 1253 & 59\\
 & \LLAMA & 3 & 685 & 78\\
 & \GlasgowOne & 11 & 903 & 71\\
  \midrule
$10^3$ & virtual best & 0 & 1781 & 322\\
 & \LLAMA & 22 & 1284 & 569\\
 & \GlasgowOne & 126 & 1539 & 449\\
  \midrule
$10^4$ & virtual best & 0 & 1943 & 2018\\
 & \LLAMA & 186 & 1771 & 3342\\
 & \GlasgowTwo & 683 & 1855 & 2701\\
  \midrule
$10^5$ & virtual best & 0 & 2045 & 14348\\
 & \LLAMA & 1346 & 2022 & 17231\\
 & \GlasgowTwo & 3019 & 1988 & 17368\\
  \midrule
$10^6$ & virtual best & 0 & 2111 & 108060\\
 & \LLAMA & 10826 & 2087 & 120459\\
 & \GlasgowTwo & 22729 & 2063 & 130789\\
  \midrule
$10^7$ & virtual best & 0 & 2178 & 815577\\
 & \LLAMA & 91012 & 2156 & 908200\\
 & \GlasgowTwo & 198944 & 2129 & 1014522\\
  \midrule
$10^8$ & virtual best & 0 & 2219 & 5822809\\
 & \LLAMA & 740765 & 2204 & 6565232\\
 & \GlasgowTwo & 1969418 & 2172 & 7792227\\
\bottomrule
\end{tabular}
\vspace{1ex}
\caption{Algorithm selection performance for different timeouts.}\label{tab:resTimeouts}
\end{table}

The results show that while for the misclassification penalty, \LLAMA is always
better than the single best algorithm, for timeouts $10^2$ to $10^4$ it is worse
in terms of the number of solved instances and mean performance. The
misclassification penalty does not take the cost of computing features into
account, while the mean performance does---for these small timeouts, the cost
of computing the features dominates any improvement through algorithm selection.
Another explanation for this is that empirical runtime measurements are
inherently noisy, which affects the accuracy of the measurements and hence the
performance of the algorithm selection models particularly in this range.

\begin{table}[t]
\begin{center}
\begin{tabular}{|c||r||r|r|r||r|r|r|r||r|r|}
\hline
$t$ & \VFtwo & \multicolumn{3}{c||}{LAD} & \multicolumn{4}{c||}{\Glasgow}& VBS & $\delta$\\
&&incomplete&classic&path&1&2&3&4&&\\\hline
$10^0$ & 300 &  \cellcolor{blue!25}1126 & 661 & 599 & 386 & 95 & 39 & 12 & 1132 & 6\\\hline
$10^1$ & 1699 & 1858 & 2101 &  \cellcolor{blue!25}2287 & 2061 & 1215 & 455 & 208 & 3388 & 101\\\hline
$10^2$ & 2834 & 1912 & 3376 & 3708 &  \cellcolor{blue!25}3943 & 3344 & 2295 & 1329 & 4636 & 693\\\hline
$10^3$ & 3458 & 1918 & 4233 & 4531 &  \cellcolor{blue!25}4908 & 4763 & 4262 & 3426 & 5170 & 262\\\hline
$10^4$ & 3701 & 1919 & 4888 & 5025 & 5156 &  \cellcolor{blue!25}5253 & 5022 & 4408 & 5332 & 79\\\hline
$10^5$ & 3850 & 1919 & 5108 & 5193 & 5301 &  \cellcolor{blue!25}5377 & 5292 & 5082 & 5434 & 57\\\hline
$10^6$ & 3977 & 1919 & 5244 & 5307 & 5386 &  \cellcolor{blue!25}5452 & 5451 & 5235 & 5500 & 48\\\hline
$10^7$ & 4082 & 1919 & 5336 & 5414 & 5458 & 5517 &  \cellcolor{blue!25}5518 & 5425 & 5567 & 49\\\hline
$10^8$ & 4191 & 1919 & 5423 & 5479 & 5508 &  \cellcolor{blue!25}5561 & 5560 & 5554 & 5608 & 47\\\hline
\end{tabular}
\end{center}
\caption{Number of solved instances at different CPU time limits: Each line displays a time limit
$t$ (in milliseconds) followed by the number of instances solved within this time limit by \VFtwo,
\IncompleteLAD, classical \LAD, and \PathLAD, \Glasgow with the lengths of paths limited to 1, 2, 3 and
4, and the VBS. The best single algorithm is highlighted in blue, and the difference between VBS and
single best if displayed in the last column ($\delta$).\label{expTimeTable}}
\end{table}

Table~\ref{expTimeTable} displays the number of instances solved at different CPU time limits,
ranging from 1 to $10^8$ milliseconds. It shows us that the best single solver depends on the time
limit considered. Simple approaches like \IncompleteLAD and \VFtwo are able to solve easy instances
very quickly, in a few milliseconds. However, they are not able to solve harder instances:
\IncompleteLAD is an incomplete approach which can only detect rather trivial inconsistencies; \VFtwo
performs a basic backtracking search and is very fast on easy instances, because it does not compute
expensive invariants. Classical \LAD, \PathLAD, and the \Glasgow algorithms solve more instances than \VFtwo
and \IncompleteLAD when considering longer time limits: \SI{10}{\ms} for \LAD and \PathLAD and
\GlasgowOne, and \SI{100}{\ms} (resp. \SI{1000}{\ms} and \SI{10000}{\ms}) for \GlasgowTwo (resp.\ 3 and
4). The virtual best solver obtains much better results, showing us that the algorithms have complementary performance. The
difference between VBS and single best (column $\delta$ of Table \ref{expTimeTable}) is more
particularly important for rather small CPU time limits. In particular, VBS solves 693 more
instances than the single best (\GlasgowOne) when the limit is \SI{100}{\ms}. In many applications,
it is important to have the fastest possible algorithm. For example, in pattern recognition
applications, we often have to solve subgraph isomorphism problems for a very large number of graphs
(in order to find a pattern image in a large database of target images, for example), so that having
an algorithm that is able to solve an instance in \SI{100}{\ms} instead of \SI{1000}{\ms} makes a
big difference. Therefore, it is important to select the best algorithm for each instance.

Table~\ref{selectionvsvbs} shows the performance of our algorithm selection approach, compared to
the VBS (which is the upper bound of what an algorithm selection approach can achieve), and the
single best solver, at different CPU time limits (the single best corresponds to results highlighted
in blue in Table 1).  Comment Table 3: Mean runtime but also number of solved instances at different
CPU time limits.  Logically, \LLAMA may solve less instances than single best for small time limits
because it spends time to compute features and choose a solver, but it should be better for larger
time limits...

\begin{table}
\begin{tabular}{|l|r|rrrrrrrrr|}
&mean & \multicolumn{9}{c|}{Number of solved instances}\\
&runtime & $10^0$ &  $10^1$ &  $10^2$ &  $10^3$ &  $10^4$ &  $10^5$ &  $10^6$ &  $10^7$ &  $10^8$\\\hline
VBS & 2375.9 & 1132 & 3388 & 4636 & 5170 & 5332 & 5434 & 5500 & 5567 & 5608\\\hline
Single best & 3177.6 & 1126 & 2287 & 3943 & 4908 & 5253 & 5377 & 5452 & 5518 & 5561\\\hline
\LLAMA & 2706.3\\\hline
\end{tabular}
\caption{}\label{selectionvsvbs}
\end{table}

Add Figure 1 which compares single best at \SI{e8}{\ms}(\GlasgowTwo) with \LLAMA ?

>>>>

\usepackage{times}
\usepackage{complexity}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage{xcolor,colortbl}
\usepackage{tabularx}
\usepackage{siunitx}
\usepackage{xspace}
\usepackage{scalefnt}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[sort]{cite}
\usepackage{enumitem}
\usepackage{tikz}
\usepackage{gnuplot-lua-tikz}
\setlist{nosep}

\newcommand{\VFtwoNS}{$\textsc{Vf{\scalefont{0.8}2}}$}
\newcommand{\GlasgowNS}{$\textsc{Glasgow}$}
\newcommand{\LADNS}{$\textsc{Lad}$}
\newcommand{\IncompleteLADNS}{$\textsc{IncompleteLad}$}
\newcommand{\PathLADNS}{$\textsc{PathLad}$}
\newcommand{\GlasgowOneNS}{$\textsc{Glasgow{\scalefont{0.8}1}}$}
\newcommand{\GlasgowTwoNS}{$\textsc{Glasgow{\scalefont{0.8}2}}$}
\newcommand{\GlasgowThreeNS}{$\textsc{Glasgow{\scalefont{0.8}3}}$}
\newcommand{\GlasgowFourNS}{$\textsc{Glasgow{\scalefont{0.8}4}}$}
\newcommand{\LLAMANS}{$\textsc{Llama}$}

@@

\begin{figure}[t]
    \centering
    \input{graph-cumulative}\vspace{-0.5cm}

    \caption{Number of solved instances over CPU time for the eight algorithms we
        consider in this paper, and the virtual best solver (VBS) that shows the best
    solver on an instance by instance basis.\label{expTimeGraph}}
\end{figure}

@@

We include \VFtwo in the portfolio, as it may solve an instance given more time,
but not \IncompleteLAD.

@@
